---
title: "3_8 Lect pt.2"
output: html_notebook
---

#Designing a personal cancer vaccine

##Section 1: Protein seqs from healthy and tumor tissue

Do a muscle alignment for given lecture_18 seqs

```{r}
library(bio3d)
seqs <- read.fasta("lecture18_sequences.fa")
seqs

```

```{r}
## Calculate positional identity scores
ide <- conserv(seqs$ali, method="identity")
mutant.sites <- which(ide < 1) 
```

Going over sequence alignment...
```{r}
# could align but not necessary here
#aln <- seqaln(seqs)

# score residue conservation to find non identical sites 
## 1.0 i match, .5 is mismatch
con <- conserv(seqs, method = "identity")
#con

# which positions are not identical
which(con <1)
## [1]  41  65 213

## Exclude gap possitions from analysis
gaps <- gap.inspect(seqs)
mutant.sites <- mutant.sites[mutant.sites %in% gaps$f.inds]

## cancer specific mutant sites
mutant.sites <- mutant.sites[1:4]

## include flanking seqs
start.pos <- mutant.sites-8
end.pos <- mutant.sites +8

## resulting extraction
result.seq <- seqs$ali[,start.pos[1]:end.pos[1]]


subseq.ind <- (41-8):(41+8)

seqs$ali["P53_mutant", subseq.ind]
```

We can use these indices stored in mutant.sites to extract subsequences as required for this activity.
```{r}
# Make a "names" label for our output sequences (one per mutant)
mutant.names <- paste0(seqs$ali["P53_wt",mutant.sites],
                       mutant.sites,
                       seqs$ali["P53_mutant",mutant.sites])

mutant.names
```

Now to extract all 9-mer mutant ecompassing sequences for each mutant site. 
```{r}
## Sequence positions surounding each mutant site
start.position <- mutant.sites - 8
end.position <-  mutant.sites + 8

# Blank matrix to store sub-sequences
store.seqs <- matrix("-", nrow=length(mutant.sites), ncol=17)
rownames(store.seqs) <- mutant.names

## Extract each sub-sequence
wt.subsequence <- NULL
mutant.subsequences <- NULL
for(i in 1:length(mutant.sites)) {
  store.seqs[i,] <- seqs$ali["P53_mutant",start.pos[i]:end.pos[i]]
  wt.subsequence <- rbind(wt.subsequence, subseq()[1,])
  mutant.subsequences <- rbind(mutant.subsequences, subseq[2,])
}

store.seqs
```

Finally, output to FASTA file
```{r}
## Output a FASTA file for further analysis
write.fasta(seqs=store.seqs, ids=mutant.names, file="subsequences.fa")
```
##Sidenote: Input sequence setup
Just to try it, here we use Uniprot KRas oncogene seq as an example iput and make 4 substations at random positions.
```{r}
#library(bio3d)
## Read KRas oncogene sequence from UniProt
wt <- get.seq("P01116")

## Here we make four mutants namely: G12V, Q22N, T74S and A130V
mutant <- wt
mutant$ali[ c(12,22,74,130)] <- c("V", "N", "S", "V")

write.fasta( seqbind(wt, mutant), ids=c("wt","mutant"), file="kras-sequences.fa")
```
Check
```{r}
sessionInfo()
```


